---
title: "TCGA.DATA.UTILS R Package"
output:
  github_document:
    toc: no
  rmarkdown::html_vignette:
    toc: no
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo=FALSE, eval=FALSE}
rmarkdown::render('README.Rmd', output_dir = '..')
```

> R-package that contains functions used by tcga.data from averissimo/tcga.data releases

## Ackowledgements

This package was developed primarily by *[André Veríssimo](http://web.tecnico.ulisboa.pt/andre.verissimo/)* with support from *Marta Lopes*, *Eunice Carrasquinha* and *[Susana Vinga](http://web.tecnico.ulisboa.pt/susanavinga/)*

This work was supported by:

- [FCT](www.fct.pt), through IDMEC, under LAETA, projects *(UID/EMS/50022/2013)*;
  - Susana Vinga acknowledges support by program
 Investigador FCT *(IF/00653/2012)* from [FCT](www.fct.pt), co-funded by the European Social Fund *(ESF)* through the Operational Program Human Potential *(POPH)*;
  - André Veríssimo acknowledges support from [FCT](www.fct.pt) *(SFRH/BD/97415/2013)*.
